---
title: "Covington Connect"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: ["menu"]
    source_code: "https://github.com/covanalytics/CovData-Dashboards.git" 
---

<style>                     
.navbar {
  background-color:#46b5d2;
  border-color:black;
}
.navbar-brand {
font-weight: bold;
}

</style> 


```{r eval=TRUE, message=FALSE, warning=FALSE, cache = TRUE}

library(flexdashboard)
library(plyr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(plotly)
theme_set(theme_pubr())

load(file = "wifi.RData", .GlobalEnv)

wifi <- wifi_data
wifi$Timestamp <- ymd(wifi$Timestamp)
wifi$Date <- format(wifi$Timestamp, "%Y-%m")

#Total Registrations Count
reg_count <- wifi_data %>%
  count(wt = Registrations)
  
#Total Markerting Opt-Ins Count  
mrkt_opt_ins <- wifi_data %>%
  count(wt = `Marketing Opt-Ins`)
  
#Opt-in percentage of registrations
opt_in_pct <- round(mrkt_opt_ins[1,1]/reg_count[1,1] *100, 0)

#Total Session Count  
sess_count <-wifi_data %>%
  count(wt = Sessions)
  
#Average session time
sess_time <- round(mean(wifi_data$Time_Usage_Minutes, na.rm = TRUE), 0)

#CIPS Session Count  
cips_sess_count <-wifi_data %>%
  count(wt = Sessions_CIPS)


reg_cnt_formatted <-formatC(reg_count, 1000, format = "d", big.mark = ",")
mrkt_opt_formatted <-formatC(mrkt_opt_ins, 1000, format = "d", big.mark = ",")
sess_cnt_formatted <-formatC(sess_count, 1000, format = "d", big.mark = ",")
cips_sess_formatted <-formatC(cips_sess_count, 1000, format = "d", big.mark = ",")

```


Dashboard
===================================

Row
------------------------------------
### Registrations
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(reg_cnt_formatted, icon = "fa-wifi", color = "#46b5d2")

```

### Marketing Opt-Ins %
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(opt_in_pct, icon = "fa-info", color = "#DB5E8A" )

```

### Sessions
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(sess_cnt_formatted, icon = "fa-users", color = "#48BEDB" )

```

### Avg. Session Duration (minutes)
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(sess_time, icon = "fa-clock", color = "#DBCD32" )

```

### Student Sessions
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(cips_sess_formatted, icon = "fa-child", color = "#8F8628")

```

Row
----------------------------------------------------------------------
 

### **Monthly Wi-Fi Registrations**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Total registrations
  registration_plot <- wifi %>%
  count(Date, wt = Registrations)%>%
  mutate_at(vars(Date), list(ym))%>%
  rename(Registrations = n)%>%
  ggplot(aes(x=Date, y=Registrations))+
  geom_line(color = "#bd5734") + 
  geom_point(size = 1) +
  scale_x_date(date_minor_breaks = "1 month")+
  theme_bw()+
        theme(legend.position = "none",
        legend.title = element_blank(),
        axis.ticks.x = element_line(colour = "black"),
        axis.text = element_text(size = 7), 
        axis.title = element_text(size =9),
        panel.grid.major = element_line(colour = "#D4D2D3"))
  

ggplotly(registration_plot)%>%
  config(displayModeBar = F)

```

Row
----------------------------------------------------------------------
### **Monthly Wi-Fi Sessions**

```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

session_plot <- wifi %>%
  count(Date, wt = Sessions)%>%
  mutate_at(vars(Date), list(ym))%>%
  rename(Sessions = n)%>%
  ggplot(aes(x=Date, y=Sessions))+
  geom_line(color = "#00802b") + 
  geom_point(size = 1) +
  scale_x_date(date_minor_breaks = "1 month")+
  theme_bw()+
        theme(legend.position = "none",
        legend.title = element_blank(),
        axis.ticks.x = element_line(colour = "black"),
        axis.text = element_text(size = 7), 
        axis.title = element_text(size =9),
        panel.grid.major = element_line(colour = "#D4D2D3"))


ggplotly(session_plot)%>%
  config(displayModeBar = F)
```

Project Description
===================================

Column
-------------------------------------------------------------------

### Project Description 

Covington Connect is an aggressive effort to smash the digital divide in Covington by expanding access to free public Wi-Fi through much of the City.

Covington Connect is a collaborative effort involving the City of Covington, Cincinnati Bell, the Housing Authority of Covington (HAC), Covington Independent Public Schools, Renaissance Covington, local computer firms Blair Technology Group and ReGadget, and Comp-U-Dopt, a Houston-based non-profit organization.

**Phase I** of the project began in 2018 with setting up 22 Wi-Fi hotspots that created zones of connectivity in the downtown area.

**Phase II** of the project began in September 2020, and added 124 Wi-Fi hotspots. These are concentrated in eight neighborhoods where the most Covington students live – Eastside, Helentown, Austinburg, Peaselburg, Levassor Park, Lewisburg, Latonia, and West Covington. 

Go to the [Covington Connect](https://www.covingtonky.gov/government/covington-connect) page on the City's website for more information

Column
----------------------------------------------------
