---
title: "Public Safety"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: yeti
    social: ["menu"]
    source_code: "https://github.com/covanalytics/CovData-Dashboards.git"
    self_contained: false
    favicon: favicon.SEAL.ico
    includes:
      in_header: GA_Script.html
---

<style>                     
.navbar {
  background-color:#46b5d2;
  border-color:black;
}
.navbar-brand {
font-weight: bold;
}


</style> 


```{r eval=TRUE, message=FALSE, warning=FALSE, cache = TRUE}

library(flexdashboard)
library(plyr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(plotly)
library(fontawesome)
theme_set(theme_pubr())

#Function to large values and add symbol
covdata_comprss <- function(tx) { 
      div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
         c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
      paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
           c("","K","M","B","T")[div], sep = "" )}


#////////////////////////////////////////////////
## Load All Police Runs Files from CovData Site /
#////////////////////////////////////////////////

##Store police file ids in vector
#file for 2017-most current year
#p_file_ids <- c("0BxZjyP_Xfv7cM1pselEtbUVmRTg", "10Ppmi-L4r84_-2hU9TqsLDhVWogymQUz","1fDmpOwOwnm6wbCSQtwQlywK7QeDJn2Ql",  "1X4Wf7_FaVwszCxetjSPPq8TWCMfG-2GA", "1mS-tptRDvfwrg5XOIilQqp1nMJDzyv4-", "1CTIqcChCexp-iITeHCiT3eT7utIN2Sty") 

#Paste file ids and download string and store in list
#dwnld_p_file_ids <- lapply(p_file_ids, function(x) paste("https://drive.google.com/uc?export=download&id=", x, sep = ""))

#Read content of each file into a list
#pruns_files <- lapply(dwnld_p_file_ids, function(x) read.csv(file = x))

#Bind list of files into a data frame
#pruns <- rbind.fill(pruns_files)

load(file = "U:/CityWide Performance/CovStat/CovStat Projects/OpenData/public_safety/police_runs.RData")

#Incident Types for police run graphics
report_categories <- c("Shooting / Gunshot Wound", "Drug Activity", "Drunk Driver / DUI",
                       "Burglary", "Robbery")

#Not Covington Runs
not_cov_runs <- c("Mutual Aid")

#Final data frame for police data graphics
#Keeping last five years
pruns_report <- pruns %>%
  mutate(YMD = format(strptime(Date_Time, format='%Y-%m-%d %H:%M:%S'), '%Y-%m-%d'),
         FY.Q = lubridate::quarter(YMD, with_year = TRUE, fiscal_start = 7),
         Qrt = paste("Q", lubridate::quarter(YMD, with_year = FALSE, fiscal_start = 7), sep = ""),
         FY_sort = as.numeric(str_sub(FY.Q, 1, 4)))%>%
  filter(FY_sort >= max(FY_sort)-4 & !(Neighborhood %in% not_cov_runs))%>%
  mutate(across(everything(), as.character),
        FY = str_sub(FY.Q, 1, 4),
        Qrt = factor(Qrt, levels = c("Q4", "Q3", "Q2", "Q1")))
 
#Quarterly Police Dept. Runs   
qrt_pruns <- pruns_report %>%
  count(FY, Incident_Type)%>%
  mutate(FY = as.numeric(FY))%>%
  arrange(desc(FY))



#//////////////////////////////////////////////
## Load Fire Runs Files ///////////////////////
#//////////////////////////////////////////////

load(file = "U:/CityWide Performance/CovStat/CovStat Projects/OpenData/public_safety/fire_runs.RData")

#Incident Types for structure fire graphics
fire_categories <- c("Structure Fire", "Ambulance Runs")

#Final data frame for fire data graphics
#Keeping last five years
fruns_report <- fruns %>%
  mutate(YMD = ymd(Date),
         FY.Q = lubridate::quarter(YMD, with_year = TRUE, fiscal_start = 7),
         Qrt = paste("Q", lubridate::quarter(YMD, with_year = FALSE, fiscal_start = 7), sep = ""),
         FY_sort = as.numeric(str_sub(FY.Q, 1, 4)))%>%
  filter(FY_sort >= max(FY_sort)-4  & !(Neighborhood %in% not_cov_runs))%>%
  mutate(across(everything(), as.character),
        FY = str_sub(FY.Q, 1, 4),
        Qrt = factor(Qrt, levels = c("Q4", "Q3", "Q2", "Q1")))


#Quarterly Fire Dept. Runs   
qrt_fruns <- fruns_report %>%
  count(FY, Incident_Description)%>%
  mutate(FY = as.numeric(FY))%>%
  arrange(desc(FY))


## Current Quarter Activity
#Count of current quarter reported shootings 
qrt_shootings <- qrt_pruns %>%
  filter(Incident_Type == report_categories[1]) %>%
  slice(1)
#Count of current quarter reported drug activity 
qrt_drugs <- qrt_pruns %>%
  filter(Incident_Type == report_categories[2]) %>%
  slice(1)
#Count of current quarter duis
qrt_dui <- qrt_pruns %>%
  filter(Incident_Type == report_categories[3]) %>%
  slice(1)
#Count of current quarter burglaries
qrt_burglary <- qrt_pruns %>%
  filter(Incident_Type == report_categories[4]) %>%
  slice(1)
#Count of current quarter burglaries
qrt_robbery <- qrt_pruns %>%
  filter(Incident_Type == report_categories[5]) %>%
  slice(1)

#Count of current quarter ambulance runs
qrt_ambulance <- qrt_fruns %>%
  filter(Incident_Description == fire_categories[2]) %>%
  slice(1)
#Count of current quarter ambulance runs
qrt_fire <- qrt_fruns %>%
  filter(Incident_Description == fire_categories[1]) %>%
  slice(1)


```


Dashboard
===================================

Row
------------------------------------

### Reported Shootings
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_shootings[1,3], icon = "fa-gavel" , color = "#46b5d2")

```

### Drug Activity Responses
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_drugs[1,3], icon = "fa-capsules", color = "#46b5d2" )

```

### Ambulance Runs
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(covdata_comprss(qrt_ambulance[1,3]), icon = "fa-briefcase-medical", color = "#ef3b92" )

```

### Structure Fires
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_fire[1,3], icon = "fa-fire-extinguisher", color = "#ef3b92")

```

### Drunk Driver / DUIs
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_dui[1,3], icon = "fa-car", color = "#46b5d2" )

```

### Reported Burglaries
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_burglary[1,3], icon = "fa-dollar", color = "#46b5d2")

```

### Reported Robberies
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(qrt_robbery[1,3], icon = "fa-dollar", color = "#46b5d2")

```


Row 
-----------------------------------------------------------------------

### **Reported Shootings**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Keep reported shootings
shootings <- pruns_report %>%
  filter(Incident_Type == report_categories[1])

#Making plot
shootings_plot <- shootings %>%
  count(FY, Qrt)%>%
  dplyr::rename(Shootings = n)
  
covdata_stacked_bar <- function(df, aes_x, aes_y, aes_fill, aes_label, legend_position = "none"){
  ggplot(df, aes(x={{aes_x}}, y={{aes_y}}, fill={{aes_fill}}))+
  geom_bar(stat = 'identity')+
  scale_fill_manual(values=c('#935b31', '#d28246', '#318693', '#469cd2'))+
  geom_text(aes(label=paste0(scales::comma({{aes_label}}, accuracy = 1))), size = 3.2, position= position_stack(0.5), size = 2.4)+
  theme_bw()+
  scale_y_continuous(label=scales::label_number_si())+  
  theme(legend.position = legend_position,
        legend.title = element_blank(),
        axis.title = element_blank())
} 

shootings_plot <- covdata_stacked_bar(shootings_plot, FY, Shootings, Qrt, Shootings, "right")

#Interactive plot
covdata_ggplotly <- function(ggplot_graph){
ggplotly(ggplot_graph, tooltip = c("x", "y"))%>%
  layout(legend = list(orientation = "v"),
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))%>%
  config(displayModeBar = F)
}

shootings_plot <- covdata_ggplotly(shootings_plot)
shootings_plot


```


### **Drug Activity Responses**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Keep reported drug activity
drug_activity <- pruns_report %>%
  filter(Incident_Type == report_categories[2])

#Making plot
drugs_plot <- drug_activity %>%
  count(FY, Qrt)%>%
  dplyr::rename(Drug.Activity = n)
  
drugs_plot <- covdata_stacked_bar(drugs_plot, FY, Drug.Activity, Qrt, Drug.Activity )  
drugs_plot <- covdata_ggplotly(drugs_plot)
drugs_plot

```


### **Ambulance Runs**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Making plot
ambulance_plot <- fruns_report %>%
  filter(Incident_Description == fire_categories[2])%>%
  count(FY, Qrt)%>%
  dplyr::rename(Amb.Runs = n)

ambulance_plot <- covdata_stacked_bar(ambulance_plot, FY, Amb.Runs, Qrt, Amb.Runs)
ambulance_plot <- covdata_ggplotly(ambulance_plot)
ambulance_plot

```


Row
-----------------------------------------------------------------------

### **Structure Fires**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Making plot
fires_plot <- fruns_report %>%
  filter(Incident_Description == fire_categories[1])%>%
  count(FY, Qrt)%>%
  dplyr::rename(Str.Fires = n)

fires_plot <- covdata_stacked_bar(fires_plot, FY, Str.Fires, Qrt, Str.Fires)
fires_plot <- covdata_ggplotly(fires_plot)
fires_plot

```


### **Drunk Driver / DUI**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Keep drunk driver / dui runs
dui <- pruns_report %>%
  filter(Incident_Type == report_categories[3])

#Making plot
dui_plot <- dui %>%
 count(FY, Qrt)%>%
 dplyr::rename(DUIs = n)

dui_plot <- covdata_stacked_bar(dui_plot, FY, DUIs, Qrt, DUIs)
dui_plot <- covdata_ggplotly(dui_plot)
dui_plot

```


### **Reported Burglaries**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Keep reported drug activity
burglaries <- pruns_report %>%
  filter(Incident_Type == report_categories[4])

#Making plot
burglary_plot <- burglaries %>%
  count(FY, Qrt)%>%
  dplyr::rename(Burglaries = n)

burglary_plot <- covdata_stacked_bar(burglary_plot, FY, Burglaries, Qrt, Burglaries)
burglarly_plot <- covdata_ggplotly(burglary_plot)
burglarly_plot

```

### **Reported Robberies**
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Keep reported drug activity
robberies <- pruns_report %>%
  filter(Incident_Type == report_categories[5])

#Making plot
robbery_plot <- robberies %>%
  count(FY, Qrt)%>%
  dplyr::rename(Robberies = n)

robbery_plot <- covdata_stacked_bar(robbery_plot, FY, Robberies, Qrt, Robberies)
robbery_plot <- covdata_ggplotly(robbery_plot)
robbery_plot
   

```


Description
===================================

Column
-------------------------------------------------------------------

###

**Data**---Police, Fire and EMS responses are the events captured in an agency's Computer-Aided Dispatch (CAD) system used to facilitate police, fire or EMS services.  The data is displayed by quarters within fiscal years and is updated monthly.  Color tiles in the dashboard display totals for the current fiscal year.\

*Structure Fires include*\

* Building fires
* Chimney or flue fires
* Cooking fires
* Fires in structures other than in a building
* Fuel burner/boiler malfunctions
* Trash or rubbish fires

**Fiscal Year Quarters**\

* Q1: July - September
* Q2: October - December
* Q3: January - March
* Q4: April - June


*Last Update: `r Sys.Date()`*


