---
title: "Growing Economy"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: yeti
    social: ["facebook", "linkedin", "twitter"]
    source_code: "https://github.com/covanalytics/CovData-Dashboards.git"
    self_contained: false
    favicon: favicon.SEAL.ico
    includes:
      in_header: GA_Script.html
---

<style>                     
.navbar {
  background-color:#46b5d2;
  border-color:black;
}
.navbar-brand {
font-weight: bold;
}

</style> 


```{r eval=TRUE, message=FALSE, warning=FALSE, cache = TRUE}

library(flexdashboard)
library(plyr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(plotly)
theme_set(theme_pubr())

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
      div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
         c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
      if(label){
        paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
           c("","K","M","B","T")[div], sep = "" )
      }
      else{
        paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
           c("","K","M","B","T")[div], sep = "" )}
      }
      

#Load ED Incentives
cov_incentives <- read.csv("cov_incentives.csv")

#Load Unincentivized jobs created / retained
load(file = "no_incentives_jobs.RData")

uncntv_job <- no_incentive_jobs %>%
  filter(FY >= max(FY)-4)

#Load Building Permits
#bld_permits<- read.csv("https://drive.google.com/uc?export=download&id=1DA2ZiG8u0P87f0rdFD4spkE_RKdcG9uF")
load(file = "bld_permits.RData")
#Load Home Purchases
home_purchases <- read.csv("real_estate_transactions.csv")

## Load Covington Unemployment Rate data downloaded from BLS
#u_rate <- read.csv("https://drive.google.com/uc?export=download&id=1D3f8vDPc06dzZQCsGBMimFboTZzaLOG9")
load(file = "u_rate.RData")

cov_incentives <- cov_incentives %>%
filter(FY >= max(FY, na.rm = TRUE) -4 | is.na(FY))

#Incentives Count
inctv_all <- cov_incentives %>%
  count()
#Amount of Direct City Incentives
inctv_city_direct <- cov_incentives %>%
  count(wt = Direct.City.Incentive)
#Amount of Leveraged Investment
inctv_leveraged <- cov_incentives %>%
  count(wt = Leveraged.Investment)
#Amount of Leveraged Investment
inctv_leveraged <- cov_incentives %>%
  count(wt = Leveraged.Investment)
#Project Net Revenue from Incentives
inctv_revenue <- cov_incentives %>%
  count(wt = Projected.Net.Revenue.over.Term)
#Jobs Created
inctv_jobs_created <- cov_incentives %>%
  count(wt = Job.Creation)%>%
  mutate(n = sum(n + sum(uncntv_job$JC)))%>%
  formatC(1000, format = "d", big.mark = ",")
#Jobs Retained
inctv_jobs_retained <- cov_incentives %>%
  count(wt = Jobs.Retained)%>%
  mutate(n = sum(n + sum(uncntv_job$JR)))


```


Dashboard {data-icon="fa-signal"}
===================================


Row
----------------------------------
 
###
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox("5-Year Totals",  icon = "", color = "#bfbfbf")

```
 
### ED Incentives 
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(inctv_all,  icon = "fa-clipboard-list", color = "#46b5d2")

```

### Direct City Incentives
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(paste("$", covdata_comprss(inctv_city_direct + 710000), sep = " "), icon = "fa-money-bill", color = "#82b74b" )

```


### Leveraged Investment
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(paste("$", covdata_comprss(inctv_leveraged), sep = " "), icon = "fa-money-bill", color = "#82b74b" )

```


### Projected Net Revenue from Incentives
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(paste("$", covdata_comprss(inctv_revenue), sep = " "), icon = "fa-money-bill", color = "#82b74b" )

```

### Jobs Created
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(inctv_jobs_created, icon = "fa-user", color = "#8F8628")

```

### Jobs Retained
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(inctv_jobs_retained +3, icon = "fa-user", color = "#8F8628")

```


Row
----------------------------------------------------------------------

### **Home Purchases**

```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

home_purchases$Date <- ymd(home_purchases$Date)
home_purchases$Date <- format(home_purchases$Date, "%Y-%m")

#home purchases by year
  purchases_plot <- home_purchases %>%
  #filter(Year >= 2018)%>%
  count(Year)%>%
  rename(Purchases = n)%>%
  mutate_at(vars(Year), as.character)%>%
  ggplot(aes(x=Year, y=Purchases))+
  geom_bar(stat = 'identity', fill = "#46b5d2")+
  ylim(c(0,800))+
  geom_text(aes(label=paste0(Purchases, "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title = element_blank())


ggplotly(purchases_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```


### **Building Permits Issued**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Building Permit Counts
permits_plot <- bld_permits %>%
  mutate_at(vars(Year), as.character)%>%
  count(Year, Main.Type)%>%
  dplyr::rename(Permits = n,
                Type = Main.Type)%>%

ggplot(aes(x=Year, y = Permits, fill = Type))+
  geom_bar(stat = 'identity', position = "dodge")+
  
  theme_bw()+
  scale_fill_manual(values=c('#A946D2','#D26346'), name = "")+
  ylim(c(0,800))+
  geom_text(aes(label=paste0(Permits, "<br>")), 
            position = position_dodge(0.9), vjust = 2,  size = 3.3, check_overlap = TRUE)+
  
  theme(legend.position = "right",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title = element_blank())


ggplotly(permits_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(legend = list(orientation = 'h'),
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))


```


### **Building Permits Value**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

## Building Permit Total Values
permits_value_plot <- bld_permits %>%
  mutate_at(vars(Year), as.character)%>%
  count(Year, Main.Type, wt = Value)%>%
  dplyr::rename(Value = n,
                Type = Main.Type)%>%
  mutate(Value_ = covdata_comprss(Value, label = TRUE))%>%

  ggplot(aes(x=Year, y = Value, fill = Type, group = Type, label = Value_))+
  geom_bar(stat = 'identity', position = "dodge")+
  
  theme_bw()+
  scale_fill_manual(values=c('#A946D2','#D26346'))+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 120000000), )+
  
  geom_text(aes(label=paste0(Value_, '<br>')), position = position_dodge(0.9), size = 3.3)+
  
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title = element_blank())

ggplotly(permits_value_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))


```

Row
----------------------------------------------------------------------
 
### **Covington Unemployment Rate %**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#unemployment rate by month and year
  unemployment_plot <- u_rate %>%
  mutate_at(vars(Date), list(ym))%>%
  mutate(`M-Y` = format(Date, "%m-%Y"))%>%
  ggplot(aes(x=Date, y=Rate, label = `M-Y`))+
  geom_line() + 
  #geom_point(size = 1) +
  scale_x_date(date_minor_breaks = "1 month")+
  theme_bw()+
        theme(legend.position = "none",
        legend.title = element_blank(),
        axis.ticks.x = element_line(colour = "black"),
        axis.text = element_text(size = 8), 
        axis.title = element_blank(),
        panel.grid.major = element_line(colour = "#D4D2D3")) 
  
ggplotly(unemployment_plot, tooltip = c("y", "label"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```



Description
===================================

Column
-------------------------------------------------------------------
###

**Economic Development (ED) Incentives**---Economic development incentives consist of financial awards, loans, and grants that are designed to attract and grow businesses in Covington. 

**Home Purchases**---Home purchases include only arms length real estate transactions involving the following properties\

* Condominiums
* Landominiums
* Single Family
* Two Family
* Three Family
* Townhomes

The source of this data is the office of the [Kenton County Property Value Administrator](https://www.kentoncounty.org/386/Property-Valuation-Administrator-PVA)

**Building Permits**---Building Permits are the authorization by the codes administration to undertake commercial or residential construction projects.  The source of this data is [Planning and Development Services of Kenton County (PDS)](https://www.pdskc.org/)\

**Unemployment Rate**---Employment data for Covington, KY is available from the [US Bureau of Labor Statistics](https://beta.bls.gov/dataViewer/view/e77bf513821e47de806930d356405286)


*Last Update: `r Sys.Date()`*



