---
title: "Thriving Neighborhoods"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: yeti
    social: ["facebook", "linkedin", "twitter"]
    source_code: "https://github.com/covanalytics/CovData-Dashboards.git"
    self_contained: false
    favicon: favicon.SEAL.ico
    includes:
      in_header: GA_Script.html

---

<style>                     
.navbar {
  background-color:#46b5d2;
  border-color:black;
}
.navbar-brand {
font-weight: bold;
}

</style> 

```{r eval=TRUE, message=FALSE, warning=FALSE, cache = TRUE}

library(flexdashboard)
library(plyr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(plotly)
library(scales)
theme_set(theme_pubr())

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx) { 
      div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
         c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
      paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
           c("","K","M","B","T")[div], sep = "" )}


#//////////////////////////////////////////////////////
## Load All Recycling Account Files from CovData Site /
#//////////////////////////////////////////////////////

##Store recycling accounts file ids in vector
#file for 2018-most current year
#r_file_ids <- c("1-sfLAEJ4GxpPS5y5e0JYeQILcXfWxNgF","1AVEN3ylVdQCeWaCBoZLe61CudPn3N7vU",  "1yONpkXuGjeeety1PGh3kn4i2VTVqCm8T", "1_mf3vC6qu9OLRtcbW4naE_ALTxpk2Oaq", "1CyL-0h0SaE7ecMVGXPKOUvM2q0Hnys8t") 

#Paste file ids and download string and store in list
#dwnld_r_file_ids <- lapply(r_file_ids, function(x) paste("https://drive.google.com/uc?export=download&id=", x, sep = ""))

#Read content of each file into a list
#recycling_files <- lapply(dwnld_r_file_ids, function(x) read.csv(file = x))

#Bind list of files into a data frame
#recycling <- rbind.fill(recycling_files)

load(file = "recycling.RData")

#Get recycling percentage by month
current_recycling <- recycling %>%
  mutate(Date = ymd(Date))
  #summarise_at(vars(c("NO", "YES", "TOTAL_ACCOUNTS")),  sum, na.rm = TRUE)%>%
  
#Get recent month recycling percentage
month_recycling <- current_recycling %>%
  arrange(desc(Date))%>%
  slice(1)%>%
  mutate(Percent = round(Recycling, 0))
  

#//////////////////////////////////////////////////////
## Load Waste Tonnage /////////////////////////////////
#//////////////////////////////////////////////////////

load(file = "tonnage.RData", .GlobalEnv)

#remove grouped_df class
tonnage <- as.data.frame(tonnage)

#get current year recycling tonnage
recycling_tonnage <- tonnage %>%
  count(FY, wt = ActTons)%>%
  arrange(desc(FY))%>%
  mutate(FY_sort = as.numeric(FY))%>%
  top_n(FY_sort, n = 5)

current_r_tons <- recycling_tonnage%>%
  slice(1)%>%
  select(2)

#//////////////////////////////////////////////////////
## Load Work Orders from Public Works and Solid Waste //
#//////////////////////////////////////////////////////

load(file = "dpw.RData")

## Pothole Repairs
pothole_repairs <- dpw %>%
  filter(grepl('5001', `Work Type`))%>%
  mutate(FY = as.character(FY))%>%
  count(FY, wt = Orders)%>%
  arrange(desc(FY))%>%
  rename(Orders = n)
  
current_pothole_repairs <- pothole_repairs %>%
  slice(1)%>%
  select(2)


## Cleanups
cleanups <- dpw %>%
  filter(grepl('Cleanup', `Work Type`))%>%
  mutate(FY = as.character(FY))%>%
  count(FY, wt = Orders)%>%
  arrange(desc(FY))%>%
  rename(Orders = n)
  
current_cleanups <- cleanups %>%
  slice(1)%>%
  select(2)

## Waste Receptacle Issues
waste_cans <- dpw %>%
  filter(grepl('300', `Work Type`))%>%
  mutate(FY = as.character(FY))%>%
  count(FY, wt = Orders)%>%
  arrange(desc(FY))%>%
  rename(Orders = n)
  #slice(1:3)

current_waste_cans <- waste_cans %>%
  slice(1)%>%
  select(2)

#//////////////////////////////////////////////////////
## Load Code Enforcement Violations  //////////////////
#//////////////////////////////////////////////////////


load(file = "code_violations.RData")

current_violations <- code_violations %>%
  slice(1) %>%
  select(2)

#Need to change at end of FY as some cases are closed retroactively  
#code_violations <- code_violations %>%
  #slice(-1)

```


Dashboard {data-icon="fa-signal"}
===================================


Row
----------------------------------

### Recycling Participation
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(paste0(month_recycling$Percent, "%", ""),  icon = "fa-recycle", color = "grey")

```

### Recycling Tonnage
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(formatC(current_r_tons, 1000, format = "d", big.mark = ","), icon = "fa-recycle", color = "#46b5d2" )

```


### Pothole Repairs
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(current_pothole_repairs, icon = "fa-road", color = "#D26346" )

```


### Cleanups
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(current_cleanups, icon = "fa-broom", color = "#d246b5" )

```

### Waste Receptacle Issues
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(current_waste_cans, icon = "fa-trash", color = "#46d2a9")

```

### Code Enf. Violations
```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

valueBox(covdata_comprss(current_violations), icon = "fa-building", color = "#b5d246")

```


Row
----------------------------------------------------------------------

### **Recycling Participation %**

```{r eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Recycling percentage by month
  recycling_plot <- current_recycling %>%
  mutate(`M-Y` = format(Date, format='%m-%Y'))%>%
  rename(Rate = Recycling)%>%
  
  ggplot(aes(x=Date, y=Rate, label = `M-Y`))+
  geom_line(color = "grey") + 
  geom_point(size = 0.6) +
  scale_x_date(date_minor_breaks = "1 month")+
  ylim(c(50, 70))+
  theme_bw()+
        theme(legend.position = "none",
        legend.title = element_blank(),
        axis.ticks.x = element_line(colour = "black"),
        #axis.text = element_text(size = 7), 
        axis.title.y = element_text(size =9),
        axis.title.x = element_blank(),
        panel.grid.major = element_line(colour = "#D4D2D3"))
  

ggplotly(recycling_plot, tooltip = c("label", "y"))%>%
 plotly::config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```

### **Recycling Tonnage**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Recycling tonnage by Fiscal Year
  tonnage_plot <- recycling_tonnage %>%
  rename(Tons = n)%>%
  mutate(Tons = round(Tons, 0))%>%
  
  ggplot(aes(x=FY, y=Tons))+
  geom_bar(stat = 'identity', fill = "#46b5d2")+
  ylim(c(0,2800))+
  geom_text(aes(label=paste0(scales::comma(Tons), "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 3000))+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title = element_blank())

ggplotly(tonnage_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         hoverinfo = 'none',
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```

### **Pothole Repairs**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Pothole Repairs by Fiscal Year
  pothole_plot <- pothole_repairs %>%
  rename(Repairs = Orders)%>%
  
  ggplot(aes(x=FY, y=Repairs))+
  geom_bar(stat = 'identity', fill = "#D26346")+
  ylim(c(0,500))+
  geom_text(aes(label=paste0(Repairs, "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title = element_blank())

ggplotly(pothole_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         hoverinfo = 'none',
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```

Row
----------------------------------------------------------------------
 
### **Cleanups**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Cleanups by Fiscal Year
  cleanups_plot <- cleanups %>%
  rename(Cleanups = Orders)%>%
  
  ggplot(aes(x=FY, y=Cleanups))+
  geom_bar(stat = 'identity', fill = "#d246b5")+
  ylim(c(0,1000))+
  geom_text(aes(label=paste0(Cleanups, "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  #ylab('orders')+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title = element_blank())

ggplotly(cleanups_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         hoverinfo = 'none',
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))

```

### **Waste Receptacle Issues**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Waste Receptacle Issues by Fiscal Year
  waste_plot <- waste_cans %>%
  rename(Issues = Orders)%>%
  
  ggplot(aes(x=FY, y=Issues))+
  geom_bar(stat = 'identity', fill = "#46d2a9")+
  ylim(c(0,1000))+
  geom_text(aes(label=paste0(Issues, "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  #ylab('orders')+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title = element_blank())

ggplotly(waste_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         hoverinfo = 'none',
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))
```

### **Code Enforcement Violations**

```{r  eval = TRUE, echo = FALSE, message = FALSE, warning=FALSE, cache=FALSE}

#Code Enforcement Violations by Fiscal Year
  code_plot <- code_violations %>%
  
  ggplot(aes(x=FY, y=Violations))+
  geom_bar(stat = 'identity', fill = "#b5d246")+
  #ylim(c(0,12000))+
  geom_text(aes(label=paste0(scales::comma(Violations), "<br>")),  position=position_nudge(0.0), size = 3.3)+
  theme_bw()+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 12000))+
  #ylab('orders')+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title = element_blank())

ggplotly(code_plot, tooltip = c("x", "y"))%>%
 config(displayModeBar = F)%>%
  layout(hoverlabel=list(bgcolor="white"),
         hoverinfo = 'none',
         xaxis=list(fixedrange=TRUE), yaxis=list(fixedrange=TRUE))
```


Description
===================================

Column
-------------------------------------------------------------------

###

\

**Recycling Participation**---Recycling is the recovery of useful materials, such as paper, glass, plastic, and metals from the trash to make new products, reducing the amount of natural materials needed. This dataset includes data on the number of recycling and non-recycling accounts\

**Recycling Tonnage**---Recycling tonnage is the recovery of useful municipal solid waste materials--consisting of everyday items we use and throw away, such as paper, glass, plastic, and metals. These items are diverted from the landfill, processed, and converted into new materials and objects.\

**Potholes Repaired**---The number of work orders completed for potholes repairs.\

**Cleanups**---These refer to general litter cleanups on streets and City-owned parks and special cleanups focused on maintaining the beauty of Covington streets and neighborhoods.\

**Waste Receptacle Issues**---These refer to missed service, overflowing status, maintenance requirements, and pedestrian usage issues for public waste receptacles\

**Code Enforcement Violations**---Covington's Code Enforcement Department ensures that the living and working environment within Covington is healthy and safe by enforcing the City's Property Maintenance, Nuisance, and Zoning Codes, which govern the proper maintenance and zoning of residential and commercial properties.  The Code Enforcement Department conducts periodic inspections of existing residential rental properties and commercial structures in an effort to ensure proper property management, which leads to the elimination of blight and the stabilization of neighborhoods.\

**Fiscal Year Quarters**\

* Q1: July - September
* Q2: October - December
* Q3: January - March
* Q4: April - June


*Last Update: `r Sys.Date()`*
